\sectionTitle{Projects}{\faCode}

\begin{experiences}

\experience
    {CAD/CAM Core Process Development (2D Contour/Chamfer/T-Slot)}
    {Introduction: Responsible for developing the core CAM module for industrial software. Implemented the complete workflow from parameter definition to toolpath calculation based on a proprietary engine and the ModuleWorks kernel.}
    {
        \begin{itemize}
            \item \textbf{Architecture Design}: Developed based on the \textbf{MVVM} architecture to thoroughly decouple UI views from business logic; Designed a universal parameter validator to ensure user input complies with physical machining constraints.
            \item \textbf{Kernel Integration}: Deeply integrated the proprietary engine with the \textbf{ModuleWorks} algorithm library; Responsible for strategy implementation and data interaction for complex processes such as 2D contour, model chamfer, helical entry, and T-slot.
            \item \textbf{Computational Geometry}: Implemented geometric analysis algorithms based on \textbf{B-Rep topology}. Developed automatic extraction of closed wireframes (Wire) on model surfaces and 3D model projection calculation, solving boundary recognition issues for complex curved surfaces.
            \item \textbf{Performance \& Robustness}: Addressed floating-point \textbf{Tolerance} issues in geometric calculations by determining the balance between performance and precision through extensive boundary testing, eliminating model tearing risks; Significantly improved projection efficiency via algorithm optimization.
        \end{itemize}
    }
    {C++, Qt, MVVM, ModuleWorks, Computational Geometry, Algorithm Optimization}
    \\*
    \\*
\experience
    {DFM Rule Library Management System}
    {Introduction: Developed a Design for Manufacturability (DFM) rule management system based on Qt/C++. Provided hierarchical rule management, parameter configuration, and persistent storage, supporting automatic verification for milling, drilling, and other scenarios.}
    {
        \begin{itemize}
            \item \textbf{Complex UI Interaction}: Implemented multi-level rule trees by overriding \textbf{QTreeView} and \textbf{QAbstractItemModel}; Used custom \textbf{Delegates} to embed controls like SpinBox/ComboBox into table cells, enabling dynamic editing of diverse rule parameters (e.g., min wall thickness, aspect ratio).
            \item \textbf{Incremental Update \& Persistence}: Designed a state tracking mechanism based on \textbf{Dirty Flags}. Maintained modification status in memory and committed only changed data (Delta) to the \textbf{SQLite} database upon saving, significantly reducing I/O overhead.
            \item \textbf{Drag \& Drop with Validation}: Implemented drag-and-drop logic based on MIME Data. By overriding \texttt{dragMoveEvent} and \texttt{dropEvent}, added hierarchical validation logic (e.g., allowing only peer sorting, prohibiting dragging parent nodes into child nodes) to ensure tree integrity.
            \item \textbf{Data Modeling}: Designed a generic rule data structure supporting extensions for multiple rule categories like "General/Milling/Drilling", and implemented import/export functionality using JSON/XML serialization.
        \end{itemize}
    }
    {C++, Qt 5, MVVM, SQLite, QTreeView, Delegate, Design Pattern} \\

\end{experiences}